Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: 
  revealjs: 
    html-math-method: 
      method: mathjax
      url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    df-print: paged
editor: visual

---

@@

    ::: {.incremental}

    :::

@@

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank (*k*=1)
    -   Efficacy: 1 through $n$ are salient ranks (*k*=n)
:::

@@

>>>>

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: 
  revealjs: 
    embed-resources: true
    theme: [default, styles.scss]
    # theme: [serif, styles.scss]
    html-math-method: 
      method: mathjax
      url: "https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js"
    df-print: paged
editor: visual
---

@@

    ::: incremental
    -   What is considered "best"?

    -   A good tournament: top *k* teams produced by the tournament matches closely to the true top *k*
    :::

@@

::: fragment
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank (*k*=1)
    -   Efficacy: 1 through $n$ are salient ranks (*k*=n)
:::

@@

<!-- ## References {.smaller} -->
